### 2016-02-18 ch03-lrm/nonparametric.tex
More outline added
Some future work stuffies + labels
Add Milgram quote

\chapter{Non-parametric modeling}

\TODO{import LRM paper}
\TODO{import Mikaya LPMTrunc paper}

>>>>

\chapter{Non-parametric modeling}
\def\thisDir{ch03-lrm}
\label{sec:nonparametric}

\myEpigraph{The essence in obedience consists in the fact that a person comes to view himself as an instrument for carrying out another person's wishes and he therefore no longer regards himself as responsible for his actions.}{Stanley Milgram}{Obedience to Authority}

\section{\TODO{LPM}}
\section{\TODO{LRM}}
\TODO{import LRM paper}
\section{\TODO{LPM with impulse response truncation}}
\input{\thisDir/LPMSmooth_ML_EG_JS_JL.tex}

\section{\TODO{Bias-variance trade-off }}
\TODO{import LRM paper}

\subsection{\TODO{Tuning rules}}
\subsubsection{\TODO{Tuning using an Oracle}}
\subsubsection{\TODO{Cross-validation}}

\subsection{\TODO{Application}}

\subsubsection{\TODO{AVIS}}
\subsubsection{\TODO{F16}}
